\documentclass[a4paper]{article}
\usepackage[top=3cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Mr P Sharp / Remove / investigations.pdf}
\title{Investigation Write-ups}
\author{Mr P. Sharp}
\date{}
\begin{document}
\maketitle \thispagestyle{fancy}
Writing up experiments is an important skill and is also essential preparation for your coursework. You should divide your report into sections, exactly what goes where is not important as long as the report reads well. The following suggested layout includes the kinds of questions you should consider when writing your report.

\subsection*{Experimental aims and method}
\begin{itemize}
    \item What is the underlying physics behind your experiment?
    \item What are the key variables you are measuring and which are you keeping constant?
    \item Are there any risks associated with your experiment and if so then what steps have you taken to mitigate them?
    \item What techniques have you used to reduce uncertainty and the chance of error?
    \item How did you decide on the range of data you collected and the number of repeats?
\end{itemize}

\subsection*{Results}
\begin{itemize}
    \item Do your tables show your results clearly and to appropriate precision?
    \item Is it clear what your graph is aiming to test or demonstrate?
    \item Is your graph correctly arranged to have a straight best fit line?
    \item Is the uncertainty on your graph communicated clearly?
    \item Does the best fit line give a relevant quantity?  Is the value of that quantity clear?
\end{itemize}

\subsection*{Analysis and conclusion}
\begin{itemize}
    \item Does your data allow you to propose or confirm the relationship between your variables?
    \item Are you able to measure any constants off your graph?  If so, have you cross-checked your results with those available elsewhere?
    \item Have you allowed for random uncertainty and systematic errors in your analysis?  What effect do these have on your conclusions?
    \item What were the limitations of your procedure?  Could these be overcome in future?
\end{itemize}
\end{document}
